Response to Reviewers - Article 4780

### 2023-06-19 review/B-response.Rmd
re-formatted response

---
title: "Response to reviewers article 4780"
subtitle: "cubble: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data"
author: "H. Sherry Zhang, Dianne Cook, Ursula Laa, Nicolas Langrené, Patricia Menéndez"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

We provide an overall summary of the changes made to the paper and the package before addressing reviewers' comments point-by-point.

# Summary of Main Changes

## The Paper:

@@

## The Package:

@@

In the point-by-point response to reviewers' comments below, the original comments are in black and our responses are in red.

@@

## The Paper

@@

## The Package

@@

## Further suggestion

@@

## The Manuscript

@@

## The package

>>>>

---
title: "Response to Reviewers - Article 4780"
subtitle: "cubble: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data"
author: "H. Sherry Zhang, Dianne Cook, Ursula Laa, Nicolas Langrené, Patricia Menéndez"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

We provide an overall summary of the changes made to the paper and the package and then we make a point-by-point explanation of how we addressed the reviewers' comments.

# Summary of the changes

## Paper

@@

## Software

@@

\bigskip
\bigskip
\hrule

\bigskip
\bigskip

Reviewers' comments are in black and \textcolor{purple}{our responses are in red}.

@@

## Paper

@@

## Software

@@

## Further suggestions

@@

## Paper

@@

## Software
